What's in a Name? Linear Temporal Logic Literally Represents Time Lines

### 2023-01-01 paper/main.tex
minor change

Our tool, \tool, uses a remarkably simple algorithm: transforming an input \ltl\ formula through a sequence of automaton and regular expression-based intermediate representations, and is surprisingly effective at providing small representations for a range of \ltl formulas. It would visualize the above air traffic control requirement behavior with the following timeline:
\begin{figure}[!h]
    \centering
    \includegraphics[width=\textwidth]{examples/ex14/ex14.png}
    \caption{[TODO: make fig with variables, explain a, b or just use oscillating example if that's easier]}
\end{figure}

@@

\begin{example}
    Zhao and Rozier~\cite{ZR14} presents a model verification specification says ``[i]f a TSAFE command is sent to an aircraft, controller/AutoResolver should then hand off the control of this aircraft'' which corresponds to \ltl\ formula
    \begin{align*}
        \always (\texttt{tsafe.TSAFE\_command1} \land \texttt{controller.CTR\_control\_1} \\
        \limplies \nextt (\neg \texttt{controller.CTR\_control\_1}))
    \end{align*}
    For simplicity, we swap the concrete atomic proposition to $a,b$ and get
    \[
        \always (a \land b \limplies \nextt (\neg b))
    \]
    For this \ltl\ formula, our tool generates the timeline representation in \cref{fig:ex14}.
    \begin{figure}[h!]
        \centering
        \includegraphics[scale=0.3]{examples/ex14/ex14.png}
        \caption{Timeline for $\always (a \land b \limplies \nextt (\neg b))$}
        \label{fig:ex14}
    \end{figure}
\end{example}

>>>>

Our tool, \tool, uses a remarkably simple algorithm: transforming an input \ltl\ formula through a sequence of automaton and regular expression-based intermediate representations, and is surprisingly effective at providing small representations for a range of \ltl\ formulas. It would visualize the above air traffic control requirement behavior with the timeline shown in \cref{example:air}.

@@

\begin{example} \label{example:air}
    Zhao and Rozier~\cite{ZR14} presents a model verification specification says ``[i]f a TSAFE command is sent to an aircraft, controller/AutoResolver should then hand off the control of this aircraft'' which corresponds to \ltl\ formula
    \begin{align*}
        \always (\texttt{tsafe.TSAFE\_command1} \land \texttt{controller.CTR\_control\_1} \\
        \limplies \nextt (\neg \texttt{controller.CTR\_control\_1}))
    \end{align*}
    For simplicity, we swap the concrete atomic proposition to $a,b$ and get
    \[
        \always (a \land b \limplies \nextt (\neg b))
    \]
    For this \ltl\ formula, our tool generates the timeline representation in \cref{fig:ex14}.
    \begin{figure}[h!]
        \centering
        \includegraphics[scale=0.3]{examples/ex14/ex14.png}
        \caption{Timeline for $\always (a \land b \limplies \nextt (\neg b))$}
        \label{fig:ex14}
    \end{figure}
\end{example}
